Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-17 Documentation/manuscript.Rnw
Manuscript edits.

  return(set)

}
@

@@

<<>>=
load("~/designedmissingnessGit/Results/tables20180509_60_1_high.RData")
high <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_med.RData")
med <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_low.RData")
low <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

>>>>

  return(set)
}
@

@@

<<echo=FALSE>>=
load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),type="latex", comment = FALSE)

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
low <- d
